### 2021-01-25 paper/intro.tex
Related work paragraph
Wordsmithing

Let $\aReg$--$\bReg$ range over thread-local registers and $\aLoc$-$\cLoc$
range over shared memory references.

@@

For single-threaded programs, memory can be thought of as you might
expect: programs write to, and read from, memory references.
This can be thought of as a total order of reads and writes,
where each read has a matching \emph{fulfilling} write,
for example:
  \begin{gather*}
    \THREAD{x\GETS0\SEMI x\GETS1\SEMI y\GETS2\SEMI
    r\GETS y\SEMI s\GETS x}
    \\[-.4ex]
    \nonumber
    \hbox{\begin{tikzinline}[node distance=1.5em]
        \event{wx0}{\DW{x}{0}}{}
        \event{wx1}{\DW{x}{1}}{right=of wx0}
        \event{wy2}{\DW{y}{2}}{right=of wx1}
        \event{ry2}{\DR{y}{2}}{right=of wy2}
        \event{rx1}{\DR{x}{1}}{right=of ry2}
        \rf[out=20,in=160]{wy2}{ry2}
        \rf[out=20,in=160]{wx1}{rx1}
        \po{wx0}{wx1}
        \po{wx1}{wy2}
        \po{wy2}{ry2}
        \po{ry2}{rx1}
      \end{tikzinline}}
  \end{gather*}

@@

>>>>

@@

For single-threaded programs, memory can be thought of as you might
expect: programs write to, and read from, memory references.
This can be thought of as a total order of reads and writes,
where each read has a matching \emph{fulfilling} write,
for example:
  \begin{gather*}
    \THREAD{x\GETS0\SEMI x\GETS1\SEMI y\GETS2\SEMI
    r\GETS y\SEMI s\GETS x}
    \\[-.4ex]
    \nonumber
    \hbox{\begin{tikzinline}[node distance=1.5em]
        \event{wx0}{\DW{x}{0}}{}
        \event{wx1}{\DW{x}{1}}{right=of wx0}
        \event{wy2}{\DW{y}{2}}{right=of wx1}
        \event{ry2}{\DR{y}{2}}{right=of wy2}
        \event{rx1}{\DR{x}{1}}{right=of ry2}
        \rf[out=20,in=160]{wy2}{ry2}
        \rf[out=20,in=160]{wx1}{rx1}
        \po{wx0}{wx1}
        \po{wx1}{wy2}
        \po{wy2}{ry2}
        \po{ry2}{rx1}
      \end{tikzinline}}
  \end{gather*}
(In examples, $\aReg$--$\bReg$ range over thread-local registers and $\aLoc$-$\cLoc$
range over shared memory references.)

@@

As far as we are aware, there are no previous attempts to provide a
compositional semantics of sequential composition in a relaxed memory model.
For a discussion of related work for relaxed memory models in general, see
\cite{DBLP:journals/pacmpl/JagadeesanJR20}.
